---
title: "Exploring resistance surfaces for Simulium"
author: "Himal Shrestha"
date: "04/03/2022"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/User/OneDrive - LA TROBE UNIVERSITY/Onchocerciasis/PhD/Genomics/Code/Project codes/220128_Ghana_simulium_analysis/")
```

# Aims
- Import optimised resistance surfaces and test if they are significant
- Create current maps

## Load libraries, functions and data

```{r}
library(raster)
library(ResistanceGA)
library(sf)
library(RColorBrewer)
library(tmap)
library(ggplot2)
library(tictoc)
library(graph4lg)
library(gdistance)
library(vegan)
library(PopGenReport)
library(graph4lg)
library("parallel")
library("doParallel")
library(rgdal)
library(spatialEco)
library(climateStability)
library(tidyverse)
```

```{r, echo = FALSE, warning=TRUE, message=FALSE}
extrafont::loadfonts(device="win", quiet = T)
```

## Load data
```{r}
ghana_LG <- readRDS("data/220304_GT_sim85LG.rds")

ghana_sites_selected <- ghana_LG[[2]]
coordinates(ghana_sites_selected) <- ghana_sites_selected[,c("coords.x1", "coords.x2")]
covs_simulium <- stack("../../../Data/Ghana GIS/220228_cov_simulium.grd")
covs_selected <- c("elevation", "isothermality", "SM1315_GT_utm", "FC_GT_utm", "annual_precpitation")

covariates_selected <- covs_simulium[[covs_selected]]
covariates_list <- aggregate(covariates_selected, fact = 2, fun = mean, na.rm = TRUE)

# covariates_selected %>% values %>% summary()

reynolds_fst <- ghana_LG[[1]]
genetic_distance <- reynolds_fst/(1-reynolds_fst)
geo_dist_GT <- ghana_LG[[3]]
## Sample locations
sample.coords <- as(ghana_sites_selected,"SpatialPoints")
```

### Visualise
06 Mar, 2022
```{r}
# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
```
#### Lin Fst
```{r}
upper_tri <- get_upper_tri(genetic_distance)
upper_tri
melted_cormat <- melt(upper_tri, na.rm = TRUE) %>% mutate(across(where(is.numeric), round, 3))
ggheatmap <- ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", 
  limit = c(0,.40), space = "Lab", 
   name="Genetic distance: Pairwise Fst Linearised") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()

p_fst <- ggheatmap + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.6, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

# ggsave(plot = p_fst, filename = "docs/220306_linFst_parasite.png", device = "png", dpi = 1000, width = 6, height = 6, units = "in" )
```

#### Geodist
```{r}
upper_tri <- get_upper_tri(geo_dist_GT)
upper_tri
melted_cormat <- melt(upper_tri, na.rm = TRUE) %>% mutate(across(where(is.numeric), round, 1))
ggheatmap <- ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", 
  limit = c(0,245), space = "Lab", 
   name="Geographic distance (km)") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()

p_geo <- ggheatmap + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.6, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

# ggsave(plot = p_geo, filename = "docs/220306_geodist_sim.png", device = "png", dpi = 1000, width = 6, height = 6, units = "in" )
```

#### Mantel
```{r}
IBD_mantel <- mantel(xdis = as.dist(geo_dist_GT), ydis = as.dist(genetic_distance), permutations = 10000)
p <- scatter_dist(mat_gd = genetic_distance, mat_ld = geo_dist_GT, pts_col = "black", method = "lm") + theme_bw(base_size = 12, base_family = "Arial") + xlab("Geographic distance (km)") + ylab("Genetic distance") # ylab(expression(F[st]/(1-F[st])))
p <- p + annotate("text", x = 120, y = 0.09, label = paste0("Significance = ", round(IBD_mantel$signif,3))) + annotate("text", x = 120, y = 0.095, label = paste0("Mantel statistic r = ", round(IBD_mantel$statistic,3)))
# ggsave(plot = p, filename = "Docs/220306_fst_geodist_mantel.png", device = "png", dpi = 100, width = 6, height = 5, units = "in" )
```

- prepare for Julia call
```{r}
JULIA_HOME = 'C:/Users/User/AppData/Local/Programs/Julia-1.6.1/bin'

jl.inputs <- jl.prep(n.Pops = length(sample.coords),
                     response = lower(genetic_distance),
                     CS_Point.File = sample.coords,
                     cholmod = T,
                     JULIA_HOME = JULIA_HOME
)
```
### Load functions
+ Generate the circuit distance -------------------------------------------
+ https://stackoverflow.com/questions/56387581/converting-a-vector-in-r-into-a-lower-upper-triangular-matrix-in-specific-order

```{r}
circuit_matrix <- function(current){
  mat <- matrix(0, nrow = 4, ncol = 4)
  mat[lower.tri(mat, diag = FALSE)] <- current
  mat <- mat + t(mat)
  colnames(mat) <- rownames(mat) <- ghana_sites_selected$code
  return(mat)
}
```


## Explore ResistanceGA output
+ create dataframe to store output
```{r}
output_df <- data.frame(variables = rep(c("Elevation", "Iso thermality", "Soil moisture", "Flow accumulation", "Precipitation"), times = c(4,4,4,4,4)),
                        replicates = rep(1:4, times = 5),
                        mantel_r = NA,
                        mantel_p = NA,
                        lgMMRR_p = NA,
                        lgMMRR_r2 = NA,
                        pmantel_r = NA,
                        pmantel_p = NA)
```

### Elevation
#### Replicate 1
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_1/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_1/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
elev1_resist <- raster(paste0(read.dir,"Results/elevation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
elev1_circuit_distance <- Run_CS.jl(jl.inputs, elev1_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
elev1_circuit_matrix <- circuit_matrix(current = elev1_circuit_distance)

# cumulative current map
elev1_current <- Run_CS.jl(jl.inputs, elev1_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
elev1_mantel <- mantel(as.dist(genetic_distance), as.dist(elev1_circuit_matrix), permutations = 10000)
output_df[1, 3:4] <- c(elev1_mantel$statistic, elev1_mantel$signif)
```

+ lgrMMRR
```{r}
elev1_cost <-  list(elev1_circuit_matrix)
names(elev1_cost) <- c("elevation")
set.seed(12345)
elev1_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = elev1_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[1, 5:6] <- c(elev1_lgMMRR$mmrr.tab$tpvalue[1],elev1_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
elev1_pmantel <- mantel.partial(xdis = as.dist(elev1_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[1, 7:8] <- c(elev1_pmantel$statistic, elev1_pmantel$signif)
```

#### Replicate 2
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_2/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_2/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
elev2_resist <- raster(paste0(read.dir,"Results/elevation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
elev2_circuit_distance <- Run_CS.jl(jl.inputs, elev2_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
elev2_circuit_matrix <- circuit_matrix(current = elev2_circuit_distance)
```

```{r}
# cumulative current map
elev2_current <- Run_CS.jl(jl.inputs, elev2_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
elev2_mantel <- mantel(as.dist(genetic_distance), as.dist(elev2_circuit_matrix), permutations = 10000)
output_df[2, 3:4] <- c(elev2_mantel$statistic, elev2_mantel$signif)
```

+ lgrMMRR
```{r}
elev2_cost <-  list(elev2_circuit_matrix)
names(elev2_cost) <- c("elevation")
set.seed(12345)
elev2_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = elev2_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[2, 5:6] <- c(elev2_lgMMRR$mmrr.tab$tpvalue[1],elev2_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
elev2_pmantel <- mantel.partial(xdis = as.dist(elev2_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[2, 7:8] <- c(elev2_pmantel$statistic, elev2_pmantel$signif)
```
#### Replicate 3
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_3/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_3/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
elev3_resist <- raster(paste0(read.dir,"Results/elevation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
elev3_circuit_distance <- Run_CS.jl(jl.inputs, elev3_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
elev3_circuit_matrix <- circuit_matrix(current = elev3_circuit_distance)
```

```{r}
# cumulative current map
elev3_current <- Run_CS.jl(jl.inputs, elev3_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
elev3_mantel <- mantel(as.dist(genetic_distance), as.dist(elev3_circuit_matrix), permutations = 10000)
output_df[3, 3:4] <- c(elev3_mantel$statistic, elev3_mantel$signif)
```

+ lgrMMRR
```{r}
elev3_cost <-  list(elev3_circuit_matrix)
names(elev3_cost) <- c("elevation")
set.seed(12345)
elev3_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = elev3_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[3, 5:6] <- c(elev3_lgMMRR$mmrr.tab$tpvalue[1],elev3_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
elev3_pmantel <- mantel.partial(xdis = as.dist(elev3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[3, 7:8] <- c(elev3_pmantel$statistic, elev3_pmantel$signif)
```
#### Replicate 4
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_4/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[1],"_4/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
elev4_resist <- raster(paste0(read.dir,"Results/elevation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
elev4_circuit_distance <- Run_CS.jl(jl.inputs, elev4_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
elev4_circuit_matrix <- circuit_matrix(current = elev4_circuit_distance)
```

```{r}
# cumulative current map
elev4_current <- Run_CS.jl(jl.inputs, elev4_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
elev4_mantel <- mantel(as.dist(genetic_distance), as.dist(elev4_circuit_matrix), permutations = 10000)
output_df[4, 3:4] <- c(elev4_mantel$statistic, elev4_mantel$signif)
```

+ lgrMMRR
```{r}
elev4_cost <-  list(elev4_circuit_matrix)
names(elev4_cost) <- c("elevation")
set.seed(12345)
elev4_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = elev4_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[4, 5:6] <- c(elev4_lgMMRR$mmrr.tab$tpvalue[1],elev4_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
elev4_pmantel <- mantel.partial(xdis = as.dist(elev4_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[4, 7:8] <- c(elev4_pmantel$statistic, elev4_pmantel$signif)
```

### Isothermality
#### Replicate 1
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_1/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_1/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
ITM1_resist <- raster(paste0(read.dir,"Results/isothermality.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
ITM1_circuit_distance <- Run_CS.jl(jl.inputs, ITM1_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
ITM1_circuit_matrix <- circuit_matrix(current = ITM1_circuit_distance)
```

```{r}
# cumulative current map
ITM1_current <- Run_CS.jl(jl.inputs, ITM1_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
ITM1_mantel <- mantel(as.dist(genetic_distance), as.dist(ITM1_circuit_matrix), permutations = 10000)
output_df[5, 3:4] <- c(ITM1_mantel$statistic, ITM1_mantel$signif)
```

+ lgrMMRR
```{r}
ITM1_cost <-  list(ITM1_circuit_matrix)
names(ITM1_cost) <- c("isothermality")
set.seed(12345)
ITM1_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = ITM1_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[5, 5:6] <- c(ITM1_lgMMRR$mmrr.tab$tpvalue[1],ITM1_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
ITM1_pmantel <- mantel.partial(xdis = as.dist(ITM1_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[5, 7:8] <- c(ITM1_pmantel$statistic, ITM1_pmantel$signif)
```
#### Replicate 2
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_2/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_2/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
ITM2_resist <- raster(paste0(read.dir,"Results/isothermality.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
ITM2_circuit_distance <- Run_CS.jl(jl.inputs, ITM2_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
ITM2_circuit_matrix <- circuit_matrix(current = ITM2_circuit_distance)
```

```{r}
# cumulative current map
ITM2_current <- Run_CS.jl(jl.inputs, ITM2_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
ITM2_mantel <- mantel(as.dist(genetic_distance), as.dist(ITM2_circuit_matrix), permutations = 10000)
output_df[6, 3:4] <- c(ITM2_mantel$statistic, ITM2_mantel$signif)
```

+ lgrMMRR
```{r}
ITM2_cost <-  list(ITM2_circuit_matrix)
names(ITM2_cost) <- c("isothermality")
set.seed(12345)
ITM2_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = ITM2_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[6, 5:6] <- c(ITM2_lgMMRR$mmrr.tab$tpvalue[1],ITM2_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
ITM2_pmantel <- mantel.partial(xdis = as.dist(ITM2_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[6, 7:8] <- c(ITM2_pmantel$statistic, ITM2_pmantel$signif)
```

#### Replicate 3
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_3/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_3/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
ITM3_resist <- raster(paste0(read.dir,"Results/isothermality.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
ITM3_circuit_distance <- Run_CS.jl(jl.inputs, ITM3_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
ITM3_circuit_matrix <- circuit_matrix(current = ITM3_circuit_distance)
```

```{r}
# cumulative current map
ITM3_current <- Run_CS.jl(jl.inputs, ITM3_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
ITM3_mantel <- mantel(as.dist(genetic_distance), as.dist(ITM3_circuit_matrix), permutations = 10000)
output_df[7, 3:4] <- c(ITM3_mantel$statistic, ITM3_mantel$signif)
```

+ lgrMMRR
```{r}
ITM3_cost <-  list(ITM3_circuit_matrix)
names(ITM3_cost) <- c("isothermality")
set.seed(12345)
ITM3_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = ITM3_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[7, 5:6] <- c(ITM3_lgMMRR$mmrr.tab$tpvalue[1],ITM3_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
ITM3_pmantel <- mantel.partial(xdis = as.dist(ITM3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[7, 7:8] <- c(ITM3_pmantel$statistic, ITM3_pmantel$signif)
```

#### Replicate 4
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_4/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[2],"_4/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
ITM4_resist <- raster(paste0(read.dir,"Results/isothermality.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
ITM4_circuit_distance <- Run_CS.jl(jl.inputs, ITM4_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
ITM4_circuit_matrix <- circuit_matrix(current = ITM4_circuit_distance)
```

```{r}
# cumulative current map
ITM4_current <- Run_CS.jl(jl.inputs, ITM4_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
ITM4_mantel <- mantel(as.dist(genetic_distance), as.dist(ITM4_circuit_matrix), permutations = 10000)
output_df[8, 3:4] <- c(ITM4_mantel$statistic, ITM4_mantel$signif)
```

+ lgrMMRR
```{r}
ITM4_cost <-  list(ITM4_circuit_matrix)
names(ITM4_cost) <- c("isothermality")
set.seed(12345)
ITM4_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = ITM4_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[8, 5:6] <- c(ITM4_lgMMRR$mmrr.tab$tpvalue[1],ITM4_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
ITM4_pmantel <- mantel.partial(xdis = as.dist(ITM4_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[8, 7:8] <- c(ITM4_pmantel$statistic, ITM4_pmantel$signif)
```

+ Replicate 2 best
```{r}
# ITM_conductance <- raster.invert(ITM2_resist)
# ITM_conductance_rescaled <- rescale0to1(ITM_conductance)
```

### Soil moisture
#### Replicate 1
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_1/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_1/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
SM1_resist <- raster(paste0(read.dir,"Results/SM1315_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
SM1_circuit_distance <- Run_CS.jl(jl.inputs, SM1_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
SM1_circuit_matrix <- circuit_matrix(current = SM1_circuit_distance)
```

```{r}
# cumulative current map
SM1_current <- Run_CS.jl(jl.inputs, SM1_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
SM1_mantel <- mantel(as.dist(genetic_distance), as.dist(SM1_circuit_matrix), permutations = 10000)
output_df[9, 3:4] <- c(SM1_mantel$statistic, SM1_mantel$signif)
```

+ lgrMMRR
```{r}
SM1_cost <-  list(SM1_circuit_matrix)
names(SM1_cost) <- c("soil moisture")
set.seed(12345)
SM1_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = SM1_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[9, 5:6] <- c(SM1_lgMMRR$mmrr.tab$tpvalue[1],SM1_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
SM1_pmantel <- mantel.partial(xdis = as.dist(SM1_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[9, 7:8] <- c(SM1_pmantel$statistic, SM1_pmantel$signif)
```
#### Replicate 2
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_2/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_2/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
SM2_resist <- raster(paste0(read.dir,"Results/SM1315_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
SM2_circuit_distance <- Run_CS.jl(jl.inputs, SM2_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
SM2_circuit_matrix <- circuit_matrix(current = SM2_circuit_distance)
```

```{r}
# cumulative current map
SM2_current <- Run_CS.jl(jl.inputs, SM2_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
SM2_mantel <- mantel(as.dist(genetic_distance), as.dist(SM2_circuit_matrix), permutations = 10000)
output_df[10, 3:4] <- c(SM2_mantel$statistic, SM2_mantel$signif)
```

+ lgrMMRR
```{r}
SM2_cost <-  list(SM2_circuit_matrix)
names(SM2_cost) <- c("soil moisture")
set.seed(12345)
SM2_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = SM2_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[10, 5:6] <- c(SM2_lgMMRR$mmrr.tab$tpvalue[1],SM2_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
SM2_pmantel <- mantel.partial(xdis = as.dist(SM2_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[10, 7:8] <- c(SM2_pmantel$statistic, SM2_pmantel$signif)
```

#### Replicate 3
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_3/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_3/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
SM3_resist <- raster(paste0(read.dir,"Results/SM1315_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
SM3_circuit_distance <- Run_CS.jl(jl.inputs, SM3_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
SM3_circuit_matrix <- circuit_matrix(current = SM3_circuit_distance)
```

```{R}
# cumulative current map
SM3_current <- Run_CS.jl(jl.inputs, SM3_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
SM3_mantel <- mantel(as.dist(genetic_distance), as.dist(SM3_circuit_matrix), permutations = 10000)
output_df[11, 3:4] <- c(SM3_mantel$statistic, SM3_mantel$signif)
```

+ lgrMMRR
```{r}
SM3_cost <-  list(SM3_circuit_matrix)
names(SM3_cost) <- c("soil moisture")
set.seed(12345)
SM3_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = SM3_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[11, 5:6] <- c(SM3_lgMMRR$mmrr.tab$tpvalue[1],SM3_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
SM3_pmantel <- mantel.partial(xdis = as.dist(SM3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[11, 7:8] <- c(SM3_pmantel$statistic, SM3_pmantel$signif)
```
#### Replicate 4
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_4/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[3],"_4/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
SM4_resist <- raster(paste0(read.dir,"Results/SM1315_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
SM4_circuit_distance <- Run_CS.jl(jl.inputs, SM4_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
SM4_circuit_matrix <- circuit_matrix(current = SM4_circuit_distance)
```

```{r}
# cumulative current map
SM4_current <- Run_CS.jl(jl.inputs, SM4_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
SM4_mantel <- mantel(as.dist(genetic_distance), as.dist(SM4_circuit_matrix), permutations = 10000)
output_df[12, 3:4] <- c(SM4_mantel$statistic, SM4_mantel$signif)
```

+ lgrMMRR
```{r}
SM4_cost <-  list(SM4_circuit_matrix)
names(SM4_cost) <- c("soil moisture")
set.seed(12345)
SM4_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = SM4_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[12, 5:6] <- c(SM4_lgMMRR$mmrr.tab$tpvalue[1],SM4_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
SM4_pmantel <- mantel.partial(xdis = as.dist(SM4_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[12, 7:8] <- c(SM4_pmantel$statistic, SM4_pmantel$signif)
```
+ Replicate 3 is the best surface
```{r}
SM_conductance <- raster.invert(SM3_resist)
SM_conductance_rescaled <- rescale0to1(SM_conductance)
```

### Flow accumulation
#### Replicate 1
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_1/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_1/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FC1_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FC1_circuit_distance <- Run_CS.jl(jl.inputs, FC1_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FC1_circuit_matrix <- circuit_matrix(current = FC1_circuit_distance)
```


```{r}
# cumulative current map
FC1_current <- Run_CS.jl(jl.inputs, FC1_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
FC1_mantel <- mantel(as.dist(genetic_distance), as.dist(FC1_circuit_matrix), permutations = 10000)
output_df[13, 3:4] <- c(FC1_mantel$statistic, FC1_mantel$signif)
```

+ lgrMMRR
```{r}
FC1_cost <-  list(FC1_circuit_matrix)
names(FC1_cost) <- c("Flow accumulation")
set.seed(12345)
FC1_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FC1_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[13, 5:6] <- c(FC1_lgMMRR$mmrr.tab$tpvalue[1],FC1_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
FC1_pmantel <- mantel.partial(xdis = as.dist(FC1_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[13, 7:8] <- c(FC1_pmantel$statistic, FC1_pmantel$signif)
```
#### Replicate 2
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_2/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_2/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FC2_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FC2_circuit_distance <- Run_CS.jl(jl.inputs, FC2_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FC2_circuit_matrix <- circuit_matrix(current = FC2_circuit_distance)
```

```{r}
# cumulative current map
FC2_current <- Run_CS.jl(jl.inputs, FC2_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
FC2_mantel <- mantel(as.dist(genetic_distance), as.dist(FC2_circuit_matrix), permutations = 10000)
output_df[14, 3:4] <- c(FC2_mantel$statistic, FC2_mantel$signif)
```

+ lgrMMRR
```{r}
FC2_cost <-  list(FC2_circuit_matrix)
names(FC2_cost) <- c("Flow accumulation")
set.seed(12345)
FC2_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FC2_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[14, 5:6] <- c(FC2_lgMMRR$mmrr.tab$tpvalue[1],FC2_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
FC2_pmantel <- mantel.partial(xdis = as.dist(FC2_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[14, 7:8] <- c(FC2_pmantel$statistic, FC2_pmantel$signif)
```

#### Replicate 3
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_3/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_3/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FC3_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FC3_circuit_distance <- Run_CS.jl(jl.inputs, FC3_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FC3_circuit_matrix <- circuit_matrix(current = FC3_circuit_distance)
```

```{r}
# cumulative current map
FC3_current <- Run_CS.jl(jl.inputs, FC3_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
FC3_mantel <- mantel(as.dist(genetic_distance), as.dist(FC3_circuit_matrix), permutations = 10000)
output_df[15, 3:4] <- c(FC3_mantel$statistic, FC3_mantel$signif)
```

+ lgrMMRR
```{r}
FC3_cost <-  list(FC3_circuit_matrix)
names(FC3_cost) <- c("Flow accumulation")
set.seed(12345)
FC3_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FC3_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[15, 5:6] <- c(FC3_lgMMRR$mmrr.tab$tpvalue[1],FC3_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
FC3_pmantel <- mantel.partial(xdis = as.dist(FC3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[15, 7:8] <- c(FC3_pmantel$statistic, FC3_pmantel$signif)
```

#### Replicate 4
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_4/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[4],"_4/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FC4_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FC4_circuit_distance <- Run_CS.jl(jl.inputs, FC4_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FC4_circuit_matrix <- circuit_matrix(current = FC4_circuit_distance)
```

```{r}
# cumulative current map
FC4_current <- Run_CS.jl(jl.inputs, FC4_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
FC4_mantel <- mantel(as.dist(genetic_distance), as.dist(FC4_circuit_matrix), permutations = 10000)
output_df[16, 3:4] <- c(FC4_mantel$statistic, FC4_mantel$signif)
```

+ lgrMMRR
```{r}
FC4_cost <-  list(FC4_circuit_matrix)
names(FC4_cost) <- c("Flow accumulation")
set.seed(12345)
FC4_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FC4_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[16, 5:6] <- c(FC4_lgMMRR$mmrr.tab$tpvalue[1],FC4_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
FC4_pmantel <- mantel.partial(xdis = as.dist(FC4_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[16, 7:8] <- c(FC4_pmantel$statistic, FC4_pmantel$signif)
```

+ Replicate 1 is the best surface
```{r}
# FC_conductance <- raster.invert(FC1_resist)
# FC_conductance_rescaled <- rescale0to1(FC_conductance)

simcomposite_conductance <- SM_conductance_rescaled # * FC_conductance_rescaled
```

### Annual precipitation
#### Replicate 1
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_1/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_1/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
precip1_resist <- raster(paste0(read.dir,"Results/annual_precpitation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
precip1_circuit_distance <- Run_CS.jl(jl.inputs, precip1_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
precip1_circuit_matrix <- circuit_matrix(current = precip1_circuit_distance)
```

```{r}
# cumulative current map
precip1_current <- Run_CS.jl(jl.inputs, precip1_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
precip1_mantel <- mantel(as.dist(genetic_distance), as.dist(precip1_circuit_matrix), permutations = 10000)
output_df[17, 3:4] <- c(precip1_mantel$statistic, precip1_mantel$signif)
```

+ lgrMMRR
```{r}
precip1_cost <-  list(precip1_circuit_matrix)
names(precip1_cost) <- c("precipitation")
set.seed(12345)
precip1_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = precip1_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[17, 5:6] <- c(precip1_lgMMRR$mmrr.tab$tpvalue[1],precip1_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
precip1_pmantel <- mantel.partial(xdis = as.dist(precip1_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[17, 7:8] <- c(precip1_pmantel$statistic, precip1_pmantel$signif)
```

#### Replicate 2
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_2/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_2/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
precip2_resist <- raster(paste0(read.dir,"Results/annual_precpitation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
precip2_circuit_distance <- Run_CS.jl(jl.inputs, precip2_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
precip2_circuit_matrix <- circuit_matrix(current = precip2_circuit_distance)
```

```{r}
# cumulative current map
precip2_current <- Run_CS.jl(jl.inputs, precip2_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
precip2_mantel <- mantel(as.dist(genetic_distance), as.dist(precip2_circuit_matrix), permutations = 10000)
output_df[18, 3:4] <- c(precip2_mantel$statistic, precip2_mantel$signif)
```

+ lgrMMRR
```{r}
precip2_cost <-  list(precip2_circuit_matrix)
names(precip2_cost) <- c("precipitation")
set.seed(12345)
precip2_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = precip2_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[18, 5:6] <- c(precip2_lgMMRR$mmrr.tab$tpvalue[1],precip2_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
precip2_pmantel <- mantel.partial(xdis = as.dist(precip2_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[18, 7:8] <- c(precip2_pmantel$statistic, precip2_pmantel$signif)
```

#### Replicate 3
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_3/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_3/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
precip3_resist <- raster(paste0(read.dir,"Results/annual_precpitation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
precip3_circuit_distance <- Run_CS.jl(jl.inputs, precip3_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
precip3_circuit_matrix <- circuit_matrix(current = precip3_circuit_distance)
```

```{r}
# cumulative current map
precip3_current <- Run_CS.jl(jl.inputs, precip3_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
precip3_mantel <- mantel(as.dist(genetic_distance), as.dist(precip3_circuit_matrix), permutations = 10000)
output_df[19, 3:4] <- c(precip3_mantel$statistic, precip3_mantel$signif)
```

+ lgrMMRR
```{r}
precip3_cost <-  list(precip3_circuit_matrix)
names(precip3_cost) <- c("precipitation")
set.seed(12345)
precip3_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = precip3_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[19, 5:6] <- c(precip3_lgMMRR$mmrr.tab$tpvalue[1],precip3_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
precip3_pmantel <- mantel.partial(xdis = as.dist(precip3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[19, 7:8] <- c(precip3_pmantel$statistic, precip3_pmantel$signif)
```

#### Replicate 4
```{r}
read.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_4/")  

write.dir <- paste0("results/resistanceGA_85/220303_", names(covariates_list)[5],"_4/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
precip4_resist <- raster(paste0(read.dir,"Results/annual_precpitation.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
precip4_circuit_distance <- Run_CS.jl(jl.inputs, precip4_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
precip4_circuit_matrix <- circuit_matrix(current = precip4_circuit_distance)
```

```{r}
# cumulative current map
precip4_current <- Run_CS.jl(jl.inputs, precip4_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ Mantel test
```{r}
set.seed(12345)
precip4_mantel <- mantel(as.dist(genetic_distance), as.dist(precip4_circuit_matrix), permutations = 10000)
output_df[20, 3:4] <- c(precip4_mantel$statistic, precip4_mantel$signif)
```

+ lgrMMRR
```{r}
precip4_cost <-  list(precip4_circuit_matrix)
names(precip4_cost) <- c("precipitation")
set.seed(12345)
precip4_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = precip4_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[20, 5:6] <- c(precip4_lgMMRR$mmrr.tab$tpvalue[1],precip4_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
set.seed(12345)
precip4_pmantel <- mantel.partial(xdis = as.dist(precip4_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[20, 7:8] <- c(precip4_pmantel$statistic, precip4_pmantel$signif)
```

```{r}
output_df %>% write.csv("data/220315_sim85explore_resistance.csv")
```

+ Replicate 3 is the best
```{r}
precip_conductance <- raster.invert(precip3_resist)
precip_conductance_rescaled <- rescale0to1(precip_conductance)

simcomposite_conductance <- simcomposite_conductance * precip_conductance_rescaled

simcomposite_conductance_2 <- SM_conductance_rescaled * precip_conductance_rescaled
```

```{r}
precip_conductance %>% writeRaster("data/220305_sim85precipconductance.asc")
```

```{r}
sim85_resurfaces <- stack(precip3_resist, precip3_current)
names(sim85_resurfaces) <- c("precip_resistance", "precip_current")

sim85_resurfaces %>% writeRaster("data/220206_sim85_resurfaces.grd", overwrite = F)
```

## No smooth - Flow accumulation
17 Mar, 2022

+ create dataframe to store output
```{r}
output_df <- data.frame(variables = rep(c("FC - No smoothing"), times = c(4)),
                        replicates = rep(1:4, times = 1),
                        beta_geo = NA, 
                        geo_p = NA,
                        beta_circuit = NA,
                        circuit_p = NA,
                        pmantel_r = NA,
                        pmantel_p = NA,
                        lgMMRR_fp = NA,
                        lgMMRR_r2 = NA)
```

### Replicate 1
```{r}
read.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_1/")  

write.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_1/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FCns1_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FCns1_circuit_distance <- Run_CS.jl(jl.inputs, FCns1_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FCns1_circuit_matrix <- circuit_matrix(current = FCns1_circuit_distance)
```

```{r}
# cumulative current map
FCns1_current <- Run_CS.jl(jl.inputs, FCns1_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ lgrMMRR
```{r}
FCns1_cost <-  list(FCns1_circuit_matrix)
names(FCns1_cost) <- c("Flow accumulation -ns")
set.seed(12345)
FCns1_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FCns1_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[1, c(3:6,9:10)] <- c(FCns1_lgMMRR$mmrr.tab$coefficient[1], FCns1_lgMMRR$mmrr.tab$tpvalue[1], FCns1_lgMMRR$mmrr.tab$coefficient[2], FCns1_lgMMRR$mmrr.tab$tpvalue[2], FCns1_lgMMRR$mmrr.tab$Fpvalue[1],  FCns1_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
FCns1_pmantel <- mantel.partial(xdis = as.dist(FCns1_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[1, 7:8] <- c(FCns1_pmantel$statistic, FCns1_pmantel$signif)
```


### Replicate 2
```{r}
read.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_2/")  

write.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_2/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FCns2_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FCns2_circuit_distance <- Run_CS.jl(jl.inputs, FCns2_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FCns2_circuit_matrix <- circuit_matrix(current = FCns2_circuit_distance)
```

```{r}
# cumulative current map
FCns2_current <- Run_CS.jl(jl.inputs, FCns2_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ lgrMMRR
```{r}
FCns2_cost <-  list(FCns2_circuit_matrix)
names(FCns2_cost) <- c("Flow accumulation -ns")
set.seed(12345)
FCns2_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FCns2_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[2, c(3:6,9:10)] <- c(FCns2_lgMMRR$mmrr.tab$coefficient[2], FCns2_lgMMRR$mmrr.tab$tpvalue[2], FCns2_lgMMRR$mmrr.tab$coefficient[1], FCns2_lgMMRR$mmrr.tab$tpvalue[1], FCns2_lgMMRR$mmrr.tab$Fpvalue[1],  FCns2_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
FCns2_pmantel <- mantel.partial(xdis = as.dist(FCns2_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[2, 7:8] <- c(FCns2_pmantel$statistic, FCns2_pmantel$signif)
```


### Replicate 3
```{r}
read.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_3/")  

write.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_3/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FCns3_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FCns3_circuit_distance <- Run_CS.jl(jl.inputs, FCns3_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FCns3_circuit_matrix <- circuit_matrix(current = FCns3_circuit_distance)
```

```{r}
# cumulative current map
FCns3_current <- Run_CS.jl(jl.inputs, FCns3_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ lgrMMRR
```{r}
FCns3_cost <-  list(FCns3_circuit_matrix)
names(FCns3_cost) <- c("Flow accumulation -ns")
set.seed(12345)
FCns3_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FCns3_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[3, c(3:6,9:10)] <- c(FCns3_lgMMRR$mmrr.tab$coefficient[2], FCns3_lgMMRR$mmrr.tab$tpvalue[2], FCns3_lgMMRR$mmrr.tab$coefficient[1], FCns3_lgMMRR$mmrr.tab$tpvalue[1], FCns3_lgMMRR$mmrr.tab$Fpvalue[1],  FCns3_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
FCns3_pmantel <- mantel.partial(xdis = as.dist(FCns3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[3, 7:8] <- c(FCns3_pmantel$statistic, FCns3_pmantel$signif)
```


### Replicate 4
```{r}
read.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_4/")  

write.dir <- paste0("results/resistanceGA_85/220316_nosmooth__", names(covariates_list)[4],"_4/", "circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

```{r}
FCns4_resist <- raster(paste0(read.dir,"Results/FC_GT_utm.asc"))
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
FCns4_circuit_distance <- Run_CS.jl(jl.inputs, FCns4_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir)
FCns4_circuit_matrix <- circuit_matrix(current = FCns4_circuit_distance)
```

```{r}
# cumulative current map
FCns4_current <- Run_CS.jl(jl.inputs, FCns4_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir)
```

+ lgrMMRR
```{r}
FCns4_cost <-  list(FCns4_circuit_matrix)
names(FCns4_cost) <- c("Flow accumulation -ns")
set.seed(12345)
FCns4_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = FCns4_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[4, c(3:6,9:10)] <- c(FCns4_lgMMRR$mmrr.tab$coefficient[2], FCns4_lgMMRR$mmrr.tab$tpvalue[2], FCns4_lgMMRR$mmrr.tab$coefficient[1], FCns4_lgMMRR$mmrr.tab$tpvalue[1], FCns4_lgMMRR$mmrr.tab$Fpvalue[1],  FCns4_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
FCns4_pmantel <- mantel.partial(xdis = as.dist(FCns4_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[4, 7:8] <- c(FCns4_pmantel$statistic, FCns4_pmantel$signif)
```
```{r}
output_df %>% write.csv("data/220317_sim85explore_FCns.csv")
```


##LgrMMRR
```{r}
load("data/220315_circuit_matrix.RData")
```

```{r}
eco_cost <-  list(elev2_circuit_matrix, elev4_circuit_matrix, ITM4_circuit_matrix, SM3_circuit_matrix, FC1_circuit_matrix, precip3_circuit_matrix)
names(eco_cost) <- c("elev_IR", "elev_IM", "ITM_IR", "SM_IRM", "FC_R", "precip_IR")

eco_cost <-  list(SM3_circuit_matrix, precip3_circuit_matrix)
names(eco_cost) <- c("SM_IRM", "precip_IR")

set.seed(12345)
eco_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = eco_cost, eucl.mat = geo_dist_GT, nperm = 10000)
c(eco_lgMMRR$mmrr.tab$tpvalue[1],eco_lgMMRR$mmrr.tab$r2[1])
```


### Composite surface
```{r}
comp_resist <- simcomposite_conductance
write.dir <- paste0("results/resistanceGA/220303_", "composite_circuitscape/")
if(!dir.exists(write.dir)) dir.create(write.dir)
```

+ Generate circuit matrix and the current map

```{r}
# circuit distance
comp_circuit_distance <- Run_CS.jl(jl.inputs, comp_resist, output = "matrix", CurrentMap = F, EXPORT.dir = write.dir, is_resistance = F)
comp_circuit_matrix <- circuit_matrix(current = comp_circuit_distance)

# cumulative current map
comp_current <- Run_CS.jl(jl.inputs, comp_resist, output = "raster", CurrentMap = T, EXPORT.dir = write.dir, is_resistance = F)
```


+ lgrMMRR
```{r}
comp_cost <-  list(comp_circuit_matrix)
names(comp_cost) <- c("Comp resistance")
set.seed(12345)
comp_lgMMRR <- lgrMMRR(gen.mat = genetic_distance, cost.mats = comp_cost, eucl.mat = geo_dist_GT, nperm = 10000)
output_df[5, c(3:6,9:10)] <- c(comp_lgMMRR$mmrr.tab$coefficient[2], comp_lgMMRR$mmrr.tab$tpvalue[2], comp_lgMMRR$mmrr.tab$coefficient[1], comp_lgMMRR$mmrr.tab$tpvalue[1], comp_lgMMRR$mmrr.tab$Fpvalue[1],  comp_lgMMRR$mmrr.tab$r2[1])
```

+ partial mantel
```{r}
comp_pmantel <- mantel.partial(xdis = as.dist(comp_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
output_df[5, 7:8] <- c(comp_pmantel$statistic, comp_pmantel$signif)
```

### p-mantel
```{r}
set.seed(12345)
precip3_pmantel <- mantel.partial(xdis = as.dist(precip3_circuit_matrix), ydis = as.dist(genetic_distance), zdis = as.dist(geo_dist_GT), permutations = 10000) 
c(precip3_pmantel$statistic, precip3_pmantel$signif)
x
p <- scatter_dist(mat_gd = genetic_distance, mat_ld = comp_circuit_matrix, pts_col = "black", method = "lm") + theme_bw(base_size = 18, base_family = "Arial") + xlab("Circuit distance") + ylab("Genetic distance") # ylab(expression(F[st]/(1-F[st])))
p <- p + annotate("text", x = 2, y = 0.01, size = 6, label = paste0("Significance = ", round(comp_pmantel$signif,3))) + annotate("text", x = 2, y = 0.015, size = 6, label = paste0("partial Mantel statistic r = ", round(comp_pmantel$statistic,3)))

ggsave(plot = p, filename = "docs/220317_fst_compresist_mantel.png", device = "png", dpi = 100, width = 6, height = 5, units = "in" )
```


---------------------------------------

## Resistance surface bootstrap
```{r}

mat.list <- list(elev_commute_d, temp_commute_d, precip_commute_d, slope_commute_d, comb_commute_dist)
names(mat.list) <- c("Elevation", "Temperature", "Precipitation", "slope", "combination")
k <- c(4,4,4,4,7)

# genetic distance matrix has to be setup in a way where there is no column and row names
response <- matrix(0, 11, 11)
response[lower.tri(response)] <-  gen.dist[lower.tri(gen.dist)]

# Run bootstrap
(AIC.boot <- Resist.boot(mod.names = names(mat.list),
                         dist.mat = mat.list,
                         n.parameters = k,
                         sample.prop = 0.75,
                         iters = 1000,
                         obs = 11,
                         genetic.mat = response,
                         rank.method = c("LL")
))
```
## Combine resistance surfaces

### elevation and precipitation
```{r}
elevation <- covariates_list[[1]]
elevation <- aggregate(elevation, fact=2, fun=mean)

precipitation <- covariates_list[["precipitation"]]
precipitation <- aggregate(precipitation, fact=2, fun=mean)
precipitation <- reproj2(precipitation, elevation)

r.stack <- stack(elevation, precipitation)

PARM <- c(1, 2, 1813, 7, 0.95, 850.49)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/211210", "elev_precp", "/") 
dir.create(write.dir)

GA.inputs <- GA.prep(ASCII.dir = r.stack,
                     Results.dir = write.dir,
                     parallel = 4)

gdist.inputs <- gdist.prep(length(sp.dat), samples = sp.dat,
                             response = lower(gen.dist),
                             method = 'commuteDistance') ## Optimize using commute distance

Resist <- Combine_Surfaces(PARM = PARM,
                           gdist.inputs = gdist.inputs,
                           GA.inputs = GA.inputs,
                           out = NULL,
                           rescale = TRUE,
                           p.contribution = F)
```

```{r}
comb_commute_dist <- Run_gdistance(gdist.inputs, r = Resist)
comb_commute_dist <- comb_commute_dist %>% as.matrix()
rownames(comb_commute_dist) <- colnames(comb_commute_dist) <- colnames(reynolds_fst)

vegan::mantel(as.dist(reynolds_fst), as.dist(comb_commute_dist), permutations = 9999)

cost_d <-  list(comb_commute_dist)
names(cost_d) <- c("comb")
set.seed(12345)
lgMMRR_mod1 <- lgrMMRR(gen.mat = gen.dist, cost.mats = cost_d, eucl.mat = mat_geo_km)
lgMMRR_mod1
```


## Run Circuitscape analysis
### Altitude
```{r, eval = F}
resistance_layer <- raster("Code/Project codes/211028_Ghana_analysis/results/registanceGA/211112_elevation/Results/GHA_msk_alt.asc")
resistance_layer2 <- trim(mask( resistance_layer, bbox_buffer))
```

+ visualise the resistance layer

```{r, eval = F}
pal_res <- colorRampPalette(rev(brewer.pal(8, name = "RdYlBu")), interpolate = "linear", space = "Lab")

cond_raster <- function(resistance_layer){
  tm_shape(resistance_layer)+ 
  tm_raster(title="Resistance", alpha = 1, palette = pal_res(100), style = "cont", legend.is.portrait = T, legend.show = T)+
  tm_compass(type = "arrow", position = c(0, 0.9)) +
  tm_layout(legend.outside = T, frame = T, fontfamily = "Verdana", legend.title.fontface = 2, legend.text.size = 1)
  }

res_map <- cond_raster(resistance_layer = resistance_layer2)
# tmap_save(tm = res_map, filename = "Docs/211117_resistance_slope.png")
```


```{r, eval = F}
### rasterize the sites

resistance <- raster::extract(resistance_layer, sp.dat)
sites <- rasterize(x = sp.dat, y = resistance_layer2, field = resistance)

writeRaster(sites, "Code/Project codes/211028_Ghana_analysis/results/circuitscape/211112_elevation/sites_elev.asc", overwrite = T)
writeRaster(resistance_layer2, "Code/Project codes/211028_Ghana_analysis/results/circuitscape/211112_elevation/GT_resistance_elev.asc", overwrite = T)

# p <- bbox(eth_pts)


# Load file after circuitscape analysis -----------------------------------

cumcur_map <- raster("Code/Project codes/211028_Ghana_analysis/results/circuitscape/211112_elevation/211112_circuitscape/out_file_cum_curmap.asc")

crs(cumcur_map) <- "+proj=utm +zone=30 +datum=WGS84 +units=km +no_defs"

cumcur_map2 <- trim( mask( cumcur_map, bbox_buffer))
library(RColorBrewer)
pal <- hcl.colors(n = 100, palette = "inferno")
pal2 <- c(pal[seq(1,60, by = 3)], pal[60:100])
plot(cumcur_map2, col = pal2)


# Plot resistance map -----------------------------------------------------
proj4string(sp.dat) = CRS("+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")
gene_flow <- tm_shape(cumcur_map) +
  tm_raster(style = "cont", palette = pal2, legend.is.portrait = T, title = "Gene flow") +
  tm_layout(legend.outside = T, legend.outside.position = "right",
            frame = FALSE, fontfamily = "Verdana", legend.title.size = 1.2, legend.title.fontface = 2, legend.text.size = 1) +
  tm_shape(sp.dat) +
  tm_dots(size = 2, col = "white")
  

tmap_save(gene_flow, filename = "Docs/211117_gene_flow.png")
```
#### Plot transformation
```{r, eval = F}
resistance_layer <- raster("Code/Project codes/211028_Ghana_analysis/results/registanceGA/211118_distance_to_water_cost_d/Results/X1._gha_osm_dst_waterway_100m_2016.asc")

df <- data.frame(original_values = values(cont.rast), transformed_values = values(resistance_layer))
elev_trans <- ggplot(df, aes(original_values, transformed_values)) +
  geom_point(alpha = .05, size = 2.5) + theme_bw(base_family = "Verdana") +
  xlab("Elevation (m)") + ylab("Resistance Value") 
```

```{r, eval = F}
plot_transform <- function(cont.rast, resistance_layer, xlabel){
  df <- data.frame(original_values = values(cont.rast),
                   transformed_values = values(resistance_layer))
  plot_trans <- ggplot(df, aes(original_values, transformed_values)) +
    geom_point(alpha = .05, size = 2.5) + theme_bw(base_family = "Verdana") +
    xlab(xlabel) + ylab("Resistance Value")
  return(plot_trans)
}
```

#### Connectivity estimates: commute distance
```{r}
data <- read.csv("Code/Project codes/211028_Ghana_analysis/results/registanceGA/211112_elevation/Results/GHA_msk_alt_commuteDistance_distMat.csv", header = F)
library(gdistance)
library(vegan)
library(graph4lg)
tr <- transition(resistance_layer, transitionFunction = function(x)1/mean(x), directions = 8 )
# tr <- geoCorrection( tr, type="c", multpl=FALSE, scl=FALSE)
eDist <- as.matrix(commuteDistance( tr, sp.dat))

### Commute distance using resistanceGA
commute_dist <- Run_gdistance(gdist.inputs, r = resistance_layer)

## sanity check
ghana_sites_selected %>% select(LONG,LAT, pop_id) %>% distinct()
sp.dat %>% coordinates
reynolds_fst

rownames(eDist) <- colnames(eDist) <- colnames(reynolds_fst)
mantel_reynold_fst <- vegan::mantel(as.dist(reynolds_fst), as.dist(eDist), permutations = 9999)

p <- scatter_dist(mat_gd = reynolds_fst, mat_ld = eDist, 
             pts_col = "black", method = "lm") + theme_bw(base_size = 12, base_family = "Arial") + xlab("Ecological distance based on connectivity analysis")
ggsave(plot = p, filename = "Docs/211117_fst_geodist_ecodist.png", device = "png", dpi = 100, width = 6, height = 5, units = "in" )

```

#### Connectivity estimates: circuit distance
```{r}
data <- read.table("Code/Project codes/211028_Ghana_analysis/results/circuitscape/211112_elevation/211112_circuitscape/out_file_resistances_3columns.out",header=FALSE, sep=" ")
ctDist <- matrix(0,nrow=11,ncol=11)
for( i in 1:nrow(data)){
  ctDist[ data$V1[i], data$V2[i] ] <- data$V3[i]
}
ctDist <- ctDist + t(ctDist)
ctDist[1:5,1:5]

set.seed(999)
mantel(as.dist(fst_matrix_ghana), as.dist(ctDist), permutations = 999)
## This is not significant in Circuitscape analysis

df$circuit_distance <- ctDist[lower.tri(ctDist)]
ggplot(df,aes(x=circuit_distance,y=Genetic_Distance)) + geom_point() + 
  stat_smooth(method=lm, formula = y ~ x) + xlab("Circuit distance landcover resistance") + ylab("Genetic distance") + theme_minimal()

```

###### Annual precipitation
```{r, eval = F}
res_prec <- raster("data/210712_resistanceGA_100/annual_precp/Results/annual_precp.asc")
annual_prec <- covariates[["annual_precp"]]

prec_trans <- plot_transform(cont.rast = annual_prec, resistance_layer = res_prec, xlabel = "Annual precipitation (mm)")
```

###### Annual temperature
```{r, eval = F}
res_temp <- raster("data/210712_resistanceGA_100/annual_mean_temp/Results/annual_mean_temp.asc")
annual_temp <- covariates[["annual_mean_temp"]]/10

temp_trans <- plot_transform(cont.rast = annual_temp, resistance_layer = res_temp, xlabel =  "Annual mean temperature (C)")
```

```{r, eval = F}
png(filename = "data/210712_resistanceGA_100/transformation.png", width = 700, height = 250)
gridExtra::grid.arrange(slope_trans, prec_trans, temp_trans, nrow = 1)
dev.off()
```



### Altitude + distance to water
```{r}
resistance_layer <- raster("Code/Project codes/211028_Ghana_analysis/results/registanceGA/211116_elev_dist_3_100_iteratins/rep_1/elev.dw/elev.dw.asc")

```


## Resistance surface optimisation

```{r}
# Directory to write .asc files and results
write.dir <- "Code/Project codes/211028_Ghana_analysis/results/registanceGA/211117_elevation/"

dir.create(write.dir)

## Sample locations
sp.dat <- as(ghana_sites_selected,"SpatialPoints")
## Continuous landscape surface
cont.rast <- covariates_list[[1]]
## Genetic distance measured between sample locations (chord distance)
gen.dist <- reynolds_fst
plot(cont.rast)
plot(sp.dat, add = T, pch = 19)
```

-   Write a loop to optmise all the rasters

### Altitude

```{r}
GA.inputs <- GA.prep(ASCII.dir=cont.rast,
                     Results.dir=write.dir,
                     method = "AIC",
                     select.trans = list("A"), # set A when doing actual run
                    # seed = 12345,
                     parallel = 14,
                     maxiter = 50) # default = 1000

gdist.inputs <- gdist.prep(length(sp.dat), samples = sp.dat,
                           response = lower(gen.dist),
                           method = 'commuteDistance') ## Optimize using commute distance
# Run optimization
SS_RESULTS.gdist <- SS_optim(gdist.inputs = gdist.inputs, GA.inputs = GA.inputs)

```

```{r}
# Inverse-Reverse Monomolecular	2.167545701	1813.696449
r.tran <- Resistance.tran(transformation = "Inverse-Reverse Monomolecular", shape = 2.167545701, max = 1813.696449, r = cont.rast)
plot.t <- Plot.trans(PARM = c(2.167545701, 1813.696449), Resistance = cont.rast, transformation = "Inverse-Reverse Monomolecular")
```

## Multiple runs

### Mutiple surfaces
#### Elevation and distance to water

```{r}
reproj2 <- function(tbc, c){
  tbc <- crop(tbc,c)
  tbc <- projectRaster(tbc, c)
}
```

```{r}
elevation <- covariates_list[[1]]
elevation <- aggregate(elevation, fact=5, fun=mean)
dist_road <- covariates_list[[14]]
dist_road_1km <- aggregate(dist_road, fact=50, fun=mean)
dist_road_1km <- reproj2(dist_road_1km, elevation)
```


```{r, eval = F}
write.dir <- "Code/Project codes/211028_Ghana_analysis/results/registanceGA/211201_elev_dist_road/"
dir.create(write.dir)
cont.rast <- stack(elevation, dist_water_1km)
names(cont.rast) <- c("elev", "d_road")
gdist.inputs <- gdist.prep(length(sp.dat), samples = sp.dat,
                           response = lower(gen.dist),
                           method = 'commuteDistance')

GA.inputs <- GA.prep(ASCII.dir=cont.rast,
                     Results.dir="all.comb",
                     method = "LL",
                     select.trans = list("M", "M"), # set A when doing actual run
                     # seed = 12345,
                     parallel = 10,
                     maxiter = 50) # default = 1000

all.comb_results <- all_comb(gdist.inputs = gdist.inputs,
                             GA.inputs = GA.inputs,
                             results.dir = write.dir,
                             max.combination = 2,
                             replicate = 1,
                             dist_mod = F,
                             null_mod = F
                             )
```

```{r, eval=F}
r.tran <- Resistance.tran(transformation = "Inverse Monomolecular", shape = 10.4651, max = 1153.708, r = cont.rast)
plot.t <- Plot.trans(PARM = c(10.4651, 1153.708), Resistance = cont.rast, transformation = "Inverse Monomolecular")

```

Find more about this error

```{r}
# Error in { : 
#   task 1 failed - "no slot of name "data" for this object of class "RasterStack""
```

```{r, eval = F}
alt <- readRDS("data/210613_resistanceGA/all_comb_1623639526/rep_1/ETH_msk_alt.annual_mean_temp/ETH_msk_alt.annual_mean_temp.rds")
```

## Optimization of the single surface
```{r}
optimise_resistance <- function(cont.rast, write.dir = "Code/Project codes/211028_Ghana_analysis/results/registanceGA/"){
  GA.inputs <- GA.prep(ASCII.dir=cont.rast,
                     Results.dir=write.dir,
                     method = "AIC",
                     select.trans = list("A"), # set A when doing actual run
                     # seed = 12345,
                     parallel = 10,
                     maxiter = 100,
                     pmutation = 0.50,
                     pcrossover = 0.90) # default = 1000

  gdist.inputs <- gdist.prep(length(sp.dat), samples = sp.dat,
                             response = lower(gen.dist),
                             method = 'commuteDistance') ## Optimize using commute distance
  # Run optimization
  SS_RESULTS.gdist <- SS_optim(gdist.inputs = gdist.inputs, GA.inputs = GA.inputs)
  
  return(SS_RESULTS.gdist)
}
```

### Distance to the water
```{r}
cont.rast <- covariates_list[["distance_to_water"]] # 100m resolution - downsample otherwise take a long time
cont.rast <- aggregate(cont.rast, fact=20, fun=mean)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/211202_", names(covariates_list)[6],"_2/")  
dir.create(write.dir)
resistance_dist_road <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```

### Vegetation indices (NDVI)
```{r}
cont.rast <- covariates_list[["ndvi"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=mean)
write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[10], "_2/") 
dir.create(write.dir)
resistance_ndvi <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```


### Distance to the road
```{r}
cont.rast <- covariates_list[["dist_road"]]
cont.rast <- aggregate(cont.rast, fact=20, fun=mean)
write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[14], "_2/") 
dir.create(write.dir)
resistance_dist_road <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```



### Human population density
```{r, eval = F}
cont.rast <- covariates_list[["popden"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=mean)
write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[11], "_2/") 
dir.create(write.dir)
resistance_popden <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```


### Night time lights
```{r}
cont.rast <- covariates_list[["nightlights"]]
cont.rast <- aggregate(cont.rast, fact=20, fun=mean)
write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[5], "_2/") 
dir.create(write.dir)
resistance_nightlights <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```


### Slope
```{r}
cont.rast <- covariates_list[["slope"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=mean)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[4], "_2/") 
dir.create(write.dir)
resistance_slope <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```

### Annual average temperature
```{r}
cont.rast <- covariates_list[["temperature"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=mean)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[3], "_2/") 
dir.create(write.dir)
resistance_annual_temp <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```


### Annual precipitation
```{r}
cont.rast <- covariates_list[["precipitation"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=mean)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[2], "_2/") 
dir.create(write.dir)
tic()
resistance_dist_road <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
toc()
```


### Topographic wetness index
```{r}
cont.rast <- covariates_list[["wetness_index"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=mean)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[7], "_2/") 
dir.create(write.dir)
resistance_wetness_index <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)

```



### Land cover 
```{r}
cont.rast <- covariates_list[["land_cover"]]
cont.rast <- aggregate(cont.rast, fact=2, fun=modal)

write.dir <- paste0("Code/Project codes/211028_Ghana_analysis/results/registanceGA/", names(covariates_list)[13], "_2/") 
dir.create(write.dir)
resistance_landcover <- optimise_resistance(cont.rast = cont.rast, write.dir = write.dir)
```

### Barrier Lake
