---
title: "Ghana prevalence data from ESPEN"
author: "Himal Shrestha"
date: "23/02/2022"
output: 
  md_document:
    variant: markdown_github
    toc: yes
    toc_depth: 4
---

```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/User/OneDrive - LA TROBE UNIVERSITY/1_Projects/transition_ghana_LG/landscape_genetics_ghana")
```

## Introduction
The data is obtained from [ESPEN database](https://espen.afro.who.int/tools-resources/download-data)

## Load libraries
```{r, message=FALSE}
extrafont::loadfonts(device="win", quiet = T)
```

```{r, message=FALSE}
suppressMessages({library(sf);
  library(tidyverse);
  # library(ggplot2);
  library(rgdal);
  # library(leaflet);
  library(raster);
  library(RColorBrewer);
  # library(tmap);
  # library(gstat);
  # library(tidyr);
  library(rgeos);
  library(ggspatial);
  })
```

## Loading the data

```{r}
ghana_prev_site <- read.csv("data/data-GH-Oncho-sitelevel.csv", header = T)

ghana_prev_clean <- ghana_prev_site %>% filter(Georeliability == 1)

ghana_prev_clean2 <- ghana_prev_clean %>% dplyr::select(IU_NAME, IU_ID, LocationName, Longitude, Latitude, SurveyYear, Period, SurveyMonth, Method_0, Method_1, Method_2, Examined, Positive, Prevalence) %>% mutate(IU_NAME = as.factor(IU_NAME), IU_ID = as.numeric(IU_ID), LocationName = as.factor(LocationName), Longitude = as.numeric(Longitude), Latitude  = as.numeric(Latitude), SurveyYear = as.numeric(SurveyYear), SurveyMonth = as.factor(SurveyMonth), Period = as.factor(Period), Method_0 = as.factor(Method_0), Method_1 = as.factor(Method_1), Method_2 = as.factor(Method_2), Examined = as.numeric(Examined), Positive = as.numeric(Positive), Prevalence = as.numeric(Prevalence))

summary(ghana_prev_clean2)
# All the data from skin snipping - no REMO data

# Select the data used for mapping
ghana_prev_clean3 <- ghana_prev_clean2 %>% dplyr::select(Longitude, Latitude, SurveyYear, Period, Method_0, Examined, Positive, Prevalence) %>% mutate()

table(ghana_prev_clean3$Period, ghana_prev_clean3$Method_0)
# Most of the data that does not have the label were collected between 2006 - 2016
```

```{r}
## Ghana map boundary - level 1/updated
ghana_map_1 <- readOGR("data/gadm41_GHA_shp/gadm41_GHA_1.shp", verbose = FALSE) %>% st_as_sf()
```

### Convert to spatial object
```{r}
coordinates(ghana_prev_clean3) <- (ghana_prev_clean3[, c("Longitude","Latitude")])

ghana_prev_sf <- ghana_prev_clean3 %>% st_as_sf() 
st_crs(ghana_prev_sf) = 4326

# convert to UTM - planar CRS transformation
epsg_ghana_UTM <- 32630
st_crs(epsg_ghana_UTM)$proj4string
utm_proj_ghana <- st_crs(epsg_ghana_UTM)$proj4string  # "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs"

ghana_prev_sf <- ghana_prev_sf %>% st_transform(crs = utm_proj_ghana)
ghana_prev_sp <- as(ghana_prev_sf, "Spatial")
```


### Spatial filtering to transition region
```{r}
bbox_transition <- readRDS("data/bbox_buffer_transition_ghana.rds") %>% st_as_sf()

# filtering the prevalence data
GT_prev_sp <- intersect(x = ghana_prev_sp, y = bbox_transition)
```

```{r}
GT_prev_clean <- data.frame(GT_prev_sp)
GT_prev_clean <- GT_prev_clean %>% mutate(LONG = coords.x1, LAT = coords.x2, optional = NULL) %>% mutate(coords.x1 = NULL, coords.x2 = NULL, Longitude = NULL, Latitude = NULL)

## Omitting observations with missing data
GT_prev_clean <- na.omit(GT_prev_clean)

## Selecting only mapping data
GT_prev_mapping <- GT_prev_clean %>% filter(Method_0 == "Mapping")
```

### Find duplicate observations
```{r}
find_duplicate <- function(df){
  i <- duplicated(df[, c("LONG", "LAT")])
  long_dup <- df[i, ]$LONG
  lat_dup <- df[i, ]$LAT
  duplicate_sites <- df %>% filter(LONG %in% long_dup & LAT %in% lat_dup)
  return(duplicate_sites)
}

(duplicate_mf <- find_duplicate(df = GT_prev_mapping))
```

```{r}
GT_prev_mapdiff <- GT_prev_mapping[ !(GT_prev_mapping$LONG %in% duplicate_mf$LONG), ]
GT_prev_mapdiff %>% summary ## all collected before 2001
 
# Clean duplicate mf. If all the variables are same, keep only one observation. For, the ones with different prevalence, calculate average  
duplicate_mf2 <- duplicate_mf %>% distinct()
GT_unique_prev <- duplicate_mf2 %>% group_by(LONG, LAT) %>% summarise(Examined = sum(Examined), Positive = sum(Positive), Prevalence = Positive/Examined) 

## select required columns and merge the dataframe
GT_unique_prevmap <- GT_prev_mapdiff %>% dplyr::select(LONG, LAT, Examined, Positive, Prevalence) %>% rbind(GT_unique_prev)
```

## Visualise the prevalence data
### Prevalence histogram
```{r}
hist(GT_unique_prevmap$Prevalence, main = "",
     xlab="Onchocerciasis prevalence", ylab = ("Frequency"),
     border="black", 
     col="darkgrey", xlim=c(0,1), cex.lab=1.5, cex.axis=1, cex.main=2, cex.sub=2,
    #  ylim = c(0,225),
     las=1, 
     breaks=25)
```


### Ghana prevalence on a map
```{r}
# GT_prevmap_sf <- st_as_sf(x = GT_unique_prevmap, coords = c('LONG','LAT'), crs= "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")

ghana_map_1_sfutm <- ghana_map_1 %>% st_transform(crs = "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")
```

```{r}
mypalette <- colorRampPalette(rev(brewer.pal(11, "RdYlBu")))

p <- ggplot(ghana_map_1_sfutm) + 
  geom_sf(col = "black", lty = 1, alpha = 0.01) + coord_sf() +
  geom_sf(data = bbox_transition, alpha = 0) +
  geom_point(data = GT_unique_prevmap, aes(LONG, LAT, fill = Prevalence), color = "black", size = 2, stroke = 1, shape = 21, alpha = .7)+ labs(fill = "Onchocerciasis prevalence") +
  scale_fill_gradientn(colours = mypalette(100)) +
  scale_y_continuous(name=expression(paste("Latitude (",degree,")")), limits=c(844447.4, 973827),expand=c(0,0))+
  scale_x_continuous(name = expression(paste("Longitude (",degree,")")), limits=c(557845.6, 851520.9),expand=c(0,0)) + 
  annotation_scale(location = "br", width_hint = 0.5) +
  annotation_north_arrow(location = "tl", which_north = "true",
        pad_x = unit(0.05, "in"), pad_y = unit(0.05, "in"),
        style = north_arrow_fancy_orienteering) +
  theme_void(base_family = "Arial", base_size = 16) +
  theme(legend.position = "bottom", legend.key.size = unit(2, 'cm'), #change legend key size
        legend.key.height = unit(.5, 'cm'), #change legend key height
        legend.key.width = unit(1.5, 'cm')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5))

p
```


# Variable selection
## Loading the data
```{r}
# GT_prev <- read.csv("data/220228_GT_uniqueprev.csv")
cov_prev <- stack("data/220228_cov_prev.grd")
```

## Extract point data from raster covriates

```{r}
covs <- raster::extract(cov_prev, GT_unique_prevmap[c("LONG","LAT")], na.rm = TRUE, df = TRUE)

data_c_covs <- as.data.frame(cbind(GT_unique_prevmap, covs))
data_c_covs <- na.omit(data_c_covs)
data_c_covs %>% head()
```


## Prevalence data: Variable selection
```{r}
data_c_covs[, c("Examined", "Positive", "LONG", "LAT", "ID")] <- NULL
```

```{r}
temp_covariates <- c(names(data_c_covs)[c(3:13, 22:23)], "Prevalence")
temp_data <- data_c_covs[, temp_covariates]

precip_covariates <- c(names(data_c_covs)[14:21], "Prevalence")
precip_data <- data_c_covs[, precip_covariates]

elev_data <- data_c_covs[, c("elevation", "slope", "Prevalence")]
vegind_data <- data_c_covs[, c("EVI01_GT_utm", "NDVI01_GT_utm", "Prevalence")]
hydro_data <- data_c_covs[, c("FC_GT_utm", "TCW01_GT_utm", "SM0001_GT_utm", "distwater_GT_utm", "Prevalence")]

sociodem_data <- data_c_covs[, c("popden0001_GT_utm",
                          "housing2001_GT_utm", "nightlights0001_GT_utm", "Prevalence")]
```

```{r}
covs_prev <- data_c_covs %>% dplyr::select(annual_mean_temperature, annual_diurnal_range, temperature_seasonality, maximum_temperature_warmest_month, minimum_temperature_coldest_month, temperature_annual_range, mean_temperature_wettest_quarter, mean_temperature_driest_quarter, mean_temperature_warmest_quarter, mean_temperature_coldest_quarter, isothermality, LST_day_01, LST_night_01, annual_precpitation, precipitation_wettest_month, precipitation_driest_month, precipitation_wettest_quarter, precipitation_dreist_quarter, precipitation_warmest_quarter, precipitation_coldest_quarter, precipitation_seasonality, elevation, slope, NDVI01_GT_utm, EVI01_GT_utm, FC_GT_utm, distwater_GT_utm, TCW01_GT_utm, SM0001_GT_utm, popden0001_GT_utm, housing2001_GT_utm, nightlights0001_GT_utm)

names(covs_prev) <- c("BIO1", "BIO2", paste0("BIO",4:11), "BIO3", paste0("BIO",c(12:14,16:19)), "BIO15", "LSTD", "LSTN", "DEM", "SLP", "NDVI", "EVI", "FC", "DW", "TCW", "SM", "PD", "IHP", "NL")
```

### PCA analysis

```{r}
library(FactoMineR)
library(factoextra)

res.pca <- PCA(covs_prev, scale.unit = TRUE, graph = FALSE)
p_pca <- fviz_pca_var(res.pca, col.var = "black") + ggtitle("")
p_pca
```

```{r}
# eig.val <- get_eigenvalue(res.pca)
```
```{r}
p_scree <- fviz_eig(res.pca, addlabels = TRUE, ylim = c(0, 50)) + ggtitle("")
p_scree
```

```{r}
# var <- get_pca_var(res.pca)
```

```{r}
# p <- fviz_cos2(res.pca, choice = "var", axes = 1:3)
```


+ Upto 5 axis included because the cumulative variance explained is greater than 80%

```{r}
p_contrib <- fviz_contrib(res.pca, choice = "var", axes = 1:5, top = 100) + theme(axis.text.x = element_text(angle=90)) + ggtitle("")
p_contrib
```

