---
title: "Plot forests and parks in Ghana"
author: "Himal Shrestha"
date: "10/09/2022"
output: 
  md_document:
    variant: markdown_github
    toc: yes
    toc_depth: 4
---
```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/User/OneDrive - LA TROBE UNIVERSITY/1_Projects/transition_ghana_LG/landscape_genetics_ghana")
```

# Aim
- To plot the parks and forest reserves along with the map of Ghana

## Load libraries
```{r}
library(raster)
library(rgdal)
library(rgeos)
library(sp)
library(ggplot2)
library(sf)
library(tmap)
library(raster)
library(ggspatial)
library(ggrepel)
library(RColorBrewer)
library(ggpattern)
```

```{r}
extrafont::loadfonts(device="win", quiet = TRUE)
```

```{r}
rm(list = ls())
```

## Get Data
```{r}
# Ghana maps
ghana_map_1 <- readOGR("data/gadm41_GHA_shp/gadm41_GHA_1.shp", verbose = FALSE) %>% st_as_sf()
ghana_map_2 <- readOGR("data/gadm41_GHA_shp/gadm41_GHA_2.shp", verbose = FALSE) # %>% st_as_sf()

bbox_buffer <- readOGR("data/bbox_buffer_shp/bbox_buffer_wgs84.shp") %>% st_as_sf() %>% st_transform(crs = crs(ghana_map_1))

ghana_parks <- readOGR("data/forests_parks/Forest_and_Game_Reserves.shp", verbose = FALSE) %>% st_as_sf() %>% st_transform(crs = crs(ghana_map_1))
```

## Visualise data

- extract only Bui national park
```{r}
forest_reserves <- ghana_parks %>% dplyr::filter(Type == "Forest_reserves")
bui_np <- ghana_parks %>% dplyr::filter(ID == "Bui NP")

bui_np_crop <- st_intersection(bui_np, bbox_buffer) # crop national park to the transition region boundary
# ghana_map_1_crop <- st_intersection(ghana_map_1, bbox_buffer) # crop ghana administrative borders to the transition region boundary

# ghana_map_2_crop <- st_intersection(ghana_map_2, bbox_buffer) # crop ghana administrative borders to the transition region boundary

# plot(st_geometry(bui_np_crop))
```
### Plotting elevation
```{r}
alt_r <- raster::getData('alt', country='GHA')
alt <- trim(mask(alt_r, bbox_buffer))
slope <- raster::terrain(alt, opt='slope')
aspect <- terrain(alt, opt='aspect')

# Calculate hillshade -----------------------------------------------------
hill <- hillShade(slope, aspect, 40, 270)
```


### Get the sample information data
```{r}
sample_info <- read.csv("data/ghana_sampling_sites.csv", stringsAsFactors = TRUE)

# to identify the regions for the merged communities
sample_info <- read.csv("data/ghana_sampling_sites_2.csv", stringsAsFactors = TRUE)
```

### Getting river data
```{r}
water_lines <- readOGR("data/GHA_wat/GHA_water_lines_dcw.shp", verbose = FALSE) %>% st_as_sf() %>% st_transform(crs = crs(ghana_map_1))
water_lines_perrennial <- water_lines %>% dplyr::filter(HYC_DESCRI == "Perennial/Permanent")

water_bodies <- readOGR("data/GHA_wat/GHA_water_areas_dcw.shp", verbose = FALSE) %>% st_as_sf() %>% st_transform(crs = crs(ghana_map_1))
```

## Plot the map using ggplot2
+ Thanks to [this](https://stackoverflow.com/questions/11179666/ggplot2-raster-plotting-does-not-work-as-expected-when-setting-alpha-values)
```{r}
hs <-  hill
dem <- alt

#   Convert rasters TO dataframes for plotting with ggplot
hdf <- rasterToPoints(hs); hdf <- data.frame(hdf)
colnames(hdf) <- c("X","Y","Hill")
ddf <- rasterToPoints(dem); ddf <- data.frame(ddf)
colnames(ddf) <- c("X","Y","DEM")

#   Create vectors for colour breaks
b.hs <- seq(min(hdf$Hill),max(hdf$Hill),length.out=100)
b.dem <- seq(min(ddf$DEM),max(ddf$DEM),length.out=100)
```

```{r}
library(ggpattern)
p <- ggplot() + 
  geom_raster(data = ddf, aes(X, Y, fill = DEM, alpha = 2)) +
  geom_raster(data = hdf, aes(X, Y, alpha = Hill)) +
  scale_fill_gradientn(name="Altitude (m)",colours = terrain.colors(20))+
  guides(fill = guide_colorbar()) +
  scale_alpha(range = c(0, 0.5), guide = "none") +
  coord_equal() + theme_void()

map_data_pattern <- fortify(as_Spatial(bui_np_crop))
## Boundary
p1 <- p + 
  geom_sf(data = ghana_map_1, col = "black", lwd = 1, lty = 1, alpha = 0.01) +
  # geom_sf(data = ghana_map_2, col = "black", lwd = 1, lty = 1, alpha = 0.01)+
  # geom_sf(data = bui_np_crop, col = "black", fill = "lightcyan3", lwd = 0.5, lty = 1, alpha = .9)+
   geom_map_pattern(data = map_data_pattern,
      aes(map_id = id),
      pattern = "stripe",
      pattern_alpha = 1,
      fill   = 'lightcyan3',
      colour = 'black',
      pattern_fill = "black",
      pattern_angle = 45,
      map    = map_data_pattern
    ) +
  geom_sf(data = water_lines_perrennial, col = "steelblue", lwd = 0.8) +
  geom_sf(data = water_bodies, fill = "lightblue", col = "black", alpha = .9)+
  scale_y_continuous(name=expression(paste("Latitude (",degree,")")), limits=c(7.627786, 8.809457),expand=c(0,0))+
  scale_x_continuous(name = expression(paste("Longitude (",degree,")")), limits=c(-2.475539, 0.194787),expand=c(0,0))


scale_bar <- p1 +
  annotation_scale(location = "br", width_hint = 0.5) 

direction <- scale_bar +
  annotation_north_arrow(location = "bl", which_north = "true", 
        pad_x = unit(0.05, "in"), pad_y = unit(0.05, "in"),
        style = north_arrow_fancy_orienteering)

p3 <- direction + geom_point(data = sample_info, aes(X, Y, shape = samples), size = 3, fill = "red", alpha = .8, colour = "black", stroke = 1) +
  geom_label_repel(data = sample_info, aes(X, Y, label = pop_id), size = 5, alpha = 1) + theme_bw(base_family = "Arial", base_size = 18) + scale_shape_manual(values = c(21,24)) #, shape = 21, colour = "black", fill = "white",  alpha = 0.8) # +
  # facet_wrap(~samples, ncol = 1)


p3$labels$shape <- "Samples" #"Sample size"

ggsave(plot = p3, filename = "figs/220923_sample_locations_vec_par.png", device = "png", dpi = 500, width = 9, height = 5, units = "in" )
```

#### Vector samples
```{r}
sample_info_vectors <- sample_info %>% dplyr::filter(samples == "vectors")

vector_only <- direction + geom_point(data = sample_info_vectors, aes(X, Y, size = sample_numbers), shape = 21, fill = "white", alpha = 1, colour = "black", stroke = 1) +
  geom_label_repel(data = sample_info_vectors, aes(X, Y, label = pop_id), size = 5, alpha = 1) + theme_bw(base_family = "Arial", base_size = 18)

vector_only$labels$size <- "Sample size"

ggsave(plot = vector_only, filename = "figs/221015_sample_locations_vector_only.png", device = "png", dpi = 500, width = 9, height = 5, units = "in" )
```

#### Parasite samples
```{r}
sample_info_parasites <- sample_info %>% dplyr::filter(samples == "parasites")

parasite_only <- direction + geom_point(data = sample_info_parasites, aes(X, Y, size = sample_numbers), shape = 21, fill = "white", alpha = 1, colour = "black", stroke = 1) +
  geom_label_repel(data = sample_info_parasites, aes(X, Y, label = pop_id), size = 5, alpha = 1) + theme_bw(base_family = "Arial", base_size = 18)

parasite_only$labels$size <- "Sample size"

ggsave(plot = parasite_only, filename = "figs/221015_sample_locations_par_onlt.png", device = "png", dpi = 500, width = 9, height = 5, units = "in" )
```

### Find which locations belong to which region
```{r}
sample_info_spdf <- SpatialPointsDataFrame(coords = sample_info[,c("X", "Y")], data = sample_info,
                               proj4string = crs(ghana_map_2))

sample_info_region <- sample_info_spdf %over% ghana_map_2
sample_info_region <- sample_info_region %>% dplyr::select(NAME_1, NAME_2)

sample_info$region <- sample_info_region$NAME_1 %>% as.factor()
sample_info$district <- sample_info_region$NAME_2 %>% as.factor()
```

```{r}
sample_info %>% write.csv("data/221019_ghana_sample_stes_no_merged_com.csv")
```

```{r}
tmap_mode("view")
p_tm <- tm_shape(ghana_map_1) + tm_polygons(alpha = .01) + tm_shape(sample_info_spdf) + tm_dots()
```

```{r}
p_tm <- tm_shape(forest_reserves) + tm_polygons(alpha = .01)
```

### Plot map of Ghana
- with transition zone, riverlines and regions
```{r}
# png(filename = "Code/Project codes/docs/GT_sites.png", width = 5, height = 10, units = "in", res= 1000, bg = "transparent")
par(mfrow = c(1,1))
# plot(hill, col=grey(0:100/100), legend=FALSE, main='', axes = F, frame.plot = F, box = F)
# # plot(alt, col=hcl.colors(100, palette = "Greens", rev = F, alpha=0.35), add=TRUE)
# plot(alt, col = terrain.colors(10), alpha=0.5, add=TRUE)
plot(st_geometry(ghana_map_1))
plot(st_geometry(water_bodies), col = "lightblue", add= TRUE)

plot(st_geometry(river_line_GT_crop_wgs84), col = "lightblue", add= TRUE, lwd = 1.5)
plot(st_geometry(populations_wgs84), col = "red", pch = 17, add = TRUE)
plot(st_geometry(bbox_GT_wgs84), add = T, lwd = 2, alpha = 0.8)
# dev.off()
```

## Plot prevalence map with regions

### Preparing the prevalence data
```{r}
prev_data <- read.csv("data/220301_prev_covs.csv")

coordinates(prev_data) <- (prev_data[, c("LONG","LAT")])

prev_data_sf <- prev_data %>% st_as_sf() 
st_crs(prev_data_sf) = 32630

prev_data_sf_wgs <- prev_data_sf %>% st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs")
coordinates_prev <- data.frame(st_coordinates(prev_data_sf_wgs))

prev_data_df <- prev_data_sf_wgs %>% as.data.frame()
prev_data_df$LONG <- coordinates_prev$X
prev_data_df$LAT <- coordinates_prev$Y  
```

### Visualise data
```{r}
p <- ggplot(m_1_utm_GT_crop) +
  geom_sf(fill = "white")+ coord_sf(datum = sf::st_crs("+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs"))+
  geom_point(data = data, aes(LONG, LAT, fill = Prevalence), color = "black", size = 2, stroke = 1, shape = 21, alpha = .7)+ # plotting points with stroke
  theme_void(base_family = "Arial", base_size = 16) +
  scale_fill_gradientn(colours = mypalette(100)) +
  xlab("Logitude") + ylab("Latitude") + labs(fill = "Onchocerciasis prevalence") +
  scale_y_continuous(name=expression(paste("Latitude (",degree,")")), limits=c(844163.2, 973742.2),expand=c(0,0))+
  scale_x_continuous(name = expression(paste("Longitude (",degree,")")), limits=c(557641.1, 851721.1),expand=c(0,0)) +  annotation_scale(location = "br", width_hint = 0.5)  +
  annotation_north_arrow(location = "tl", which_north = "true",
        pad_x = unit(0, "cm"), pad_y = unit(0.2, "cm"),
        style = north_arrow_fancy_orienteering) +
  theme(legend.position = "bottom", legend.key.size = unit(2, 'cm'), #change legend key size
        legend.key.height = unit(.5, 'cm'), #change legend key height
        legend.key.width = unit(1.5, 'cm')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5))
p

ggsave(plot = p, filename = "docs/sample_sites.png", device = "png", dpi = 1000, width = 6, height = 3, units = "in", bg = "white" )
```

```{r}
mypalette <- colorRampPalette(rev(brewer.pal(11, "RdYlBu")))
p <- ggplot(ghana_map_1) + 
  geom_sf(col = "black", lty = 1, alpha = 0.01) + coord_sf() +
  geom_sf(data = bbox_buffer, alpha = 0) +
  geom_sf(data = bui_np_crop, col = "black", lty = 2, alpha = 0)+ #fill = "lightcyan3",
  # geom_sf(data = water_lines_perrennial, col = "steelblue", lwd = 0.8) +
  # geom_sf(data = water_bodies, fill = "lightblue", col = "black", alpha = .9)+
  # geom_point(data = prev_data_df, aes(LONG, LAT, fill = Prevalence), color = "black", size = 2, stroke = 1, shape = 21, alpha = .7)+ labs(fill = "Onchocerciasis prevalence") +
  scale_fill_gradientn(colours = mypalette(100)) +
  scale_y_continuous(name=expression(paste("Latitude (",degree,")")), limits=c(7.627786, 8.809457),expand=c(0,0))+
  scale_x_continuous(name = expression(paste("Longitude (",degree,")")), limits=c(-2.475539, 0.194787),expand=c(0,0)) + 
  # annotation_scale(location = "br", width_hint = 0.5) +
  # annotation_north_arrow(location = "tl", which_north = "true", 
  #       pad_x = unit(0.05, "in"), pad_y = unit(0.05, "in"),
  #       style = north_arrow_fancy_orienteering) +
  theme_void(base_family = "Arial", base_size = 16) +
  theme(legend.position = "bottom", legend.key.size = unit(2, 'cm'), #change legend key size
        legend.key.height = unit(.5, 'cm'), #change legend key height
        legend.key.width = unit(1.5, 'cm')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5))

ggsave(plot = p, filename = "figs/221015_prev_sample_sites_2.png", device = "png", dpi = 500, width = 6, height = 3, units = "in", bg = "transparent" )

ggsave(plot = p, filename = "figs/221015_for_BV_MAP.png", device = "png", dpi = 500, width = 5, height = 2.5, units = "in", bg = "transparent" )
```

